\vskip-0.6in \Large Political Uncertainty

### 2016-02-05 GS-extension.tex
add X,Y,Z defns to intuition page

\vskip.2in
Pattern more or less is to get the guy who is WHAT?
\begin{itemize}
	\item Frank: Imagine a see-saw; these guys are weights on the see-saw.
	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote)
\end{itemize}

\vskip1in
The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point
\begin{itemize}
	\item \textbf{What's the intuition for why they should be equal? Draw graph of the three PDFs in ideal point / net ideal point space}
	\item \textbf{Next question: How general is this result? That is, how much asymmetry can I have in the logistic distribution, $\beta$s, and for how broad a class of distributions would it hold? My conjecture is that it leans on having an interior single mode}
\end{itemize}

>>>>

\vskip.1in
Recall:
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 
		\end{enumerate}

\vskip.1in
Pattern more or less is to get the guy who is WHAT?
\begin{itemize}
	\item Frank: Imagine a see-saw; these guys are weights on the see-saw.
	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote)
\end{itemize}

\vskip.1in
The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point
\begin{itemize}
	\item \textbf{What's the intuition for why they should be equal? Draw graph of the three PDFs in ideal point / net ideal point space}
	\item \textbf{Next question: How general is this result? That is, how much asymmetry can I have in the logistic distribution, $\beta$s, and for how broad a class of distributions would it hold? My conjecture is that it leans on having an interior single mode}
\end{itemize}
